\TheTitle

### 2017-07-10 paper/study.tex
Addressing first set of comments in Sec. VII
Addressing the comments regarding the first few paragraphs up to the
Tasks subsection.

Also fixing the sections placing the results for each portion of the
study in the results section.

\dmg{start by describing what you mean by user study... to evaluate linvis we performed a user study...}

\dmg{and you are evaluating the visualizations, NOT the DAG}

We use a controlled mixed-methods users study in order to evaluate the
ability for the DAG to provide users with a conceptual image of how a
commit is integrated into a project, to compare the DAG and \mt models,
and determine which model the users preferred.

In this section, we describe the methods used to for designing and
implementing the user study.
\dmg{no, you describe the study, which includes the methods}

\dmg{Start by giving an overall overview of the study: the study consists of a set of tasks that users are expected to
  perform... do a top down description of what users will do
}

@@

@@

\subsection{Conceptual Tasks}
\label{sub:conceptual_tasks}

@@

\subsection{Summarization Tasks}
\label{sub:summarization_tasks}

@@

\subsection{User Opinions}
\label{sub:user_opinions}

>>>>

The purpose of the study is to quantitatively and qualitatively evaluate
the effectiveness of \tool compared to the DAG-based visualizations
found in Gitk or the git command line. The study is broken into three
task-based sections; conceptual tasks, summarization tasks, and
participant opinions. The study was performed in June of 2017 in
Kingston ON, in a controlled environment running Ubuntu 14.04. When
conducting the study, participants were allowed to use both the git
command line and Gitk together, and \tool. We will refer to Gitk in the
study, but this includes the git command line, as we recognize that git
power-users may be more comfortable with the command line than a GUI.

The primary goal of the study is to determine if \tool is more capable
of providing the participants of our study with a better conceptual
understanding of how a commit is integrated into the kernel, and a
better summarization of various metrics about the files and authors
involved with the integration. The conceptual questions are to determine
if the DAG visualization provides enough information to determine how a
commit, and any related commits, are merged into a project. \tool
displays this information directly in the form of a tree, so we will not
be performing a comparison on this section, only evaluating the results
from Gitk. The summarization tasks compare \tool and Gitk, with the
participants using one tool followed by the other on two commits from
merge-trees of differeing sizes. In both of these sections, the
participant is given a task that they are to find an answer to; we
evaluate the time it took, if the answer was correct, and how far from
the right answer they were. The user opinions provide us with a clear
comparison between the tools from the point-of-view of the participant,
providing us information about which aspects of each tool they prefered.

% TODO: Add the participant profile

@@

\subsection{Participant Profile}
\label{sub:participant_profile}

@@

\subsubsection{Conceptual Tasks}
\label{sub:conceptual_tasks}

@@

\subsubsection{Summarization Tasks}
\label{sub:summarization_tasks}

@@

\subsubsection{User Opinions}
\label{sub:user_opinions}
